Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-08 doc/JFLA2022/paper.tex
add a TODO (in the abstract)
minor correction

\begin{abstract}
  \Hydras is a collaborative library on discrete math, written for the \coq  proof assistant, and developed under the \community project. The proof scripts are
  accompanied with an electronic book, made with the help of the \alectr litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must be continuously satisfied:
   maintenance of the library with respect to several \community projects it requires and evolutions of \coq, and 
  consistency of the book with respect to the library. 
\end{abstract}

@@

 Our new proof of Theorem~\ref{thm3} is based on a systematic study of strictly decreasing sequences of ordinals below $\epsilon_0$, borrowed from Ketonen and Solovay~\cite{KS81}, and the formalization of which is described  in chapter 5 of~\cite{HydraBook}.

>>>>

\begin{abstract}
  \Hydras is a collaborative library on discrete math, written for the \coq  proof assistant, and developed under the \community project. The proof scripts are
  accompanied with an electronic book, made with the help of the \alectr litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must be continuously satisfied:
   maintenance of the library with respect to several \community projects it requires and evolutions of \coq, and 
   consistency of the book with respect to the library.
   \TODO[Pierre]{Find a better/simpler sentence about the project's structure?}
\end{abstract}

@@

 Our new proof of Theorem~\ref{thm3} is based on a systematic study of strictly decreasing sequences of ordinals below $\epsilon_0$, borrowed from Ketonen and Solovay~\cite{KS81}, and the formalization of which is described  in chapters 5 and 6 of~\cite{HydraBook}.
